Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-14 paper/intro.tex
Defined UAV acronmym

The approach is motivated, and illustrated, in a simple example. A case study applying these transformations to a UAV system that uses the Air Force Research Laboratory's OpenUxAS services for route planning is presented. Here the transforms add filters to guard against malformed input and monitors to guard against ground station spoofing and malicious flight plans from OpenUxAS. The case study system is significantly more complex than the example and shows the viability of the modeling approach to full-scale industrial design.

>>>>

The approach is motivated, and illustrated, in a simple example. A case study applying these transformations to an Unmanned Aerial Vehicle (UAV) system that uses the Air Force Research Laboratory's OpenUxAS services for route planning is presented. Here the transforms add filters to guard against malformed input and monitors to guard against ground station spoofing and malicious flight plans from OpenUxAS. The case study system is significantly more complex than the example and shows the viability of the modeling approach to full-scale industrial design.
